RadLib: a radiative heat transfer model library for CFD

### 2020-12-30 manuscript/manuscript.tex
figure size to fit
adding cost comparison results using Isaacs code and plotting tools

Figure~\ref{f:examples} shows comparative results for the different radiation models for these cases. 
%
\begin{figure}
    \begin{center}
    \begin{tabular}{c c}
        Example S1 & Example S2 \\
        \includegraphics[width=3 in]{ex_1.pdf} &
        \includegraphics[width=3 in]{ex_2b.pdf} \\
        Example S3 & Example S4 \\
        \includegraphics[width=3 in]{ex_3a.pdf} &
        \includegraphics[width=3 in]{ex_4a.pdf} \\
        Example S5 & Example B3 \\
        \includegraphics[width=3 in]{ex_5b.pdf} &
        \includegraphics[width=3 in]{ex_6.pdf}
    \end{tabular}
    \caption{Results for examples summarized in Table~\ref{t:examples}.}
    \label{f:examples}
    \end{center}
\end{figure}
%
In general, the PM model performs poorly compared to the WSSGG and RCSLW models. A notable exception is Example S4. In Example S2, the PM $q(L)/\sigma T^4$ is off scale at an essentially constant at a value of unity. The PM absorption coefficient is 27.4 atm$^{-1}$m$^{-1}$, giving optical thicknesses of 0.09 and 0.36 m in the thick and thin layers, respectively, which are relatively small compared to the isothermal domain size greater than 0.5 m. Example S5 omits the PM model to more clearly show the behavior of the WSGG and RCSLW models. For that example, the PM values follow the shape of the other curves but $Q$ varies from around -80 at $x=0$ to a peak of 200 at x=$1.5$ m, and dropping to 100 kW/m$^3$ at $x=2$ m. In all examples, four gray ($n=4$) and one clear gas are computed for the RCSLW models to give a consistent comparison to the WSGG model. Example S5 shows the sensitivity of the RCSLW model to the number of gases used. The difference between $n=2$ and $n=8$ is very small for all examples shwon, except for Example S2. When $n$ is increased from four to eight for that example the RCSLW model improves to show nearly perfect agreement with the LBL data.
In all Examples, the RCSLW model is initialized using the mean temperature and composition on the domain. In Example S5, the RCSLW model converges to the LBL solution when the model is initialized using the maximum temperature instead of the average temperature.

@@

% TODO: do the cost comparison  <13-11-20, dol> %

>>>>

Figure~\ref{f:examples} shows comparative results for the different radiation models for these cases. 
%
\begin{figure}
    \begin{center}
    \begin{tabular}{c c}
        Example S1 & Example S2 \\
        \includegraphics[width=2.75 in]{ex_1.pdf} &
        \includegraphics[width=2.75 in]{ex_2b.pdf} \\
        Example S3 & Example S4 \\
        \includegraphics[width=2.75 in]{ex_3a.pdf} &
        \includegraphics[width=2.75 in]{ex_4a.pdf} \\
        Example S5 & Example B3 \\
        \includegraphics[width=2.75 in]{ex_5b.pdf} &
        \includegraphics[width=2.75 in]{ex_6.pdf}
    \end{tabular}
    \caption{Results for examples summarized in Table~\ref{t:examples}.}
    \label{f:examples}
    \end{center}
\end{figure}
%
In general, the PM model performs poorly compared to the WSSGG and RCSLW models. A notable exception is Example S4. In Example S2, the PM $q(L)/\sigma T^4$ is off scale at an essentially constant at a value of unity. The PM absorption coefficient is 27.4 atm$^{-1}$m$^{-1}$, giving optical thicknesses of 0.09 and 0.36 m in the thick and thin layers, respectively, which are relatively small compared to the isothermal domain size greater than 0.5 m. Example S5 omits the PM model to more clearly show the behavior of the WSGG and RCSLW models. For that example, the PM values follow the shape of the other curves but $Q$ varies from around -80 at $x=0$ to a peak of 200 at x=$1.5$ m, and dropping to 100 kW/m$^3$ at $x=2$ m. In all examples, four gray ($n=4$) and one clear gas are computed for the RCSLW models to give a consistent comparison to the WSGG model. Example S5 shows the sensitivity of the RCSLW model to the number of gases used. The difference between $n=2$ and $n=8$ is very small for all examples shwon, except for Example S2. When $n$ is increased from four to eight for that example the RCSLW model improves to show nearly perfect agreement with the LBL data.
In all Examples, the RCSLW model is initialized using the mean temperature and composition on the domain. In Example S5, the RCSLW model converges to the LBL solution when the model is initialized using the maximum temperature instead of the average temperature.

@@

\subsection{Computational Cost} \label{s:cost}

A comparison was made of the computational cost of the current models implemented. Calculations were performed on a 4 GHz Quad Core Intel Core i7 iMac, version 10.15.7. Figure~\ref{f:cost}a shows the cost to compute the gas properties $k$ and $a$. This was done by timing the C++ code execution to evaluate the gas properties one million times in a loop and then averaging the results. The figure shows times normalized by the time for the WSGG model, which required 8.0E-7~s. The costs of the models, relative to WSGG, is 0.098, 1.9, 4.9, 9.4, and 18, for PM, and RCSLW with $n=1$, 2, 4, 8 gray gases, respectively. The cost of the RCSLW model is very nearly proportional to the number of gray gases considered.
%
\begin{figure}
    \begin{center}
    \begin{tabular}{c c}
        (a) & (b) \\
        \includegraphics[width=2.75 in]{fig_getka_c++.pdf} &
        \includegraphics[width=2.75 in]{fig_exS3_c++.pdf}
    \end{tabular}
    \caption{Computational cost to evaluate gas properties (a) and to run Example S3. Results are normalized by the cost of the WSSG model.}
    \label{f:cost}
    \end{center}
\end{figure}
%

Figure~\ref{f:cost}b shows the cost to evaluate Example S3. 
In this case the costs of the models, relative to WSGG, is approximately 0.75, 1.1, 1.4, 1.9, and 2.9, for PM, and RCSLW with $n=1$, 2, 4, 8 gray gases, respectively. Here, the WSGG model took 0.0079 s. In running Example S3, the costs of the various models are much more similar than in evaluating gas properties alone due to the additional overhead required in performing the calculations. In the results presented, only the cost of evaluating the solution was included; initialization and input/output costs were neglected.

Cost comparisons were also attempted with Python, but it is difficult to get meaningful results when mixing Python and C++. In particular, the cost of a single evaluation of the gas properties is small end valuating the gas properties in a Python loop results in the loop appearing to dominate the computational cost. Comparison between Python and C++ for Example S3 is somewhat more meaningful, but even here, for the six cases considered in Fig.~\ref{f:cost} the cost only varied by about 4\%. The cost of the WSGG model was 0.6~s, which is 7.6 times slower than the C++ version. It is possible that improvements in the Python speed are possible by further optimization of the Cython interface, but the Python radiative solver used in the examples is only meant to demonstrate the use of the library evaluation of gas properties.
